Tight Bounds for Online Balanced Graph Partitioning

### 2020-05-08 paper/disc20clustering.tex
wip

 \newcommand\mahmoud[1]{\color{orange}\textbf{Mahmoud: #1~}\color{black}}
 \newcommand\stefan[1]{\color{blue}\textbf{Stefan: #1}\color{black}}
 \newcommand\maciek[1]{\color{brown}\textbf{(Maciek: #1)}\color{black}}
 %\newcommand\mahmoud[1]{}
 %\newcommand\stefan[1]{}
 %\newcommand\maciek[1]{}

@@

	Finally, we are ready to bound the competitive ratio
	\begin{equation*}
		\frac{\TAlg(\sigma)}{\OPT(\sigma)} \leq \frac{11\alpha \cdot \ell + |\sigma_E|}{\alpha/2 + E/2} \leq \frac{27\alpha\cdot\ell + 2\cdot E}{\alpha + E} \leq 27 \ell = O(\ell).
	\end{equation*}

@@

	It remains to consider the last, unfinished phase.
	Consider the case, where the unfinished phase is also the first one.
	Then, we cannot charge $\OPT$ due to the inability to partition the components.
	Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
	If the input finished before the first $\alpha$ external requests, then \TAlg is $1$-competitive.
	If there were at least $\alpha$ external requests, then $\OPT$ either paid $\alpha$ for serving them remotely, or paid $\alpha$ for a migration; for the cost of \TAlg we follow the analysis of the unsaturated pairs.
	Now, consider the case, where there are at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests.
	This way, the competitive ratio increases at most twofold.
\end{proof}

>>>>

 %\newcommand\mahmoud[1]{\color{orange}\textbf{Mahmoud: #1~}\color{black}}
 \newcommand\stefan[1]{\color{blue}\textbf{Stefan: #1}\color{black}}
 %\newcommand\maciek[1]{\color{brown}\textbf{(Maciek: #1)}\color{black}}
 \newcommand\mahmoud[1]{}
 %\newcommand\stefan[1]{}
 \newcommand\maciek[1]{}

@@

	Finally, we bound the competitive ratio
	\begin{equation*}
		\frac{\TAlg(\sigma)}{\OPT(\sigma)} \leq \frac{11\alpha \cdot \ell + |\sigma_E|}{\alpha/2 + E/2} \leq \frac{27\alpha\cdot\ell + 2\cdot E}{\alpha + E} \leq 27 \ell = O(\ell).
	\end{equation*}

@@

	It remains to consider the last, unfinished phase.
	First, consider the case, where the unfinished phase is also the first one.
	Then, we cannot charge $\OPT$ due to the inability to partition the components.
	Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
	If the input finished before the first $\alpha$ external requests, then \TAlg is $1$-competitive.
	If there were at least $\alpha$ external requests, then $\OPT$ either paid $\alpha$ for serving them remotely, or paid $\alpha$ for a migration; for the cost of \TAlg we follow the analysis of the unsaturated pairs.
	Second, consider the case, where there are at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests.
	This way, the competitive ratio increases at most twofold.
\end{proof}
